Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-13 automatica/paper.tex
small change in intro

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, an approach to program
synthesis very popular in the recent years.  CEGIS denotes an
iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle. Essentially, the inductive generalisation uses information
about a limited number of inputs to make claims about all the possible
inputs in the form of candidate solutions. Our two instantiations of
CEGIS are described next.

>>>>

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, an approach to program
synthesis that became very popular in the recent years.  CEGIS denotes an
iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle. Essentially, the inductive generalisation uses information
about a limited number of inputs to make claims about all the possible
inputs in the form of candidate solutions. Our two instantiations of
CEGIS are described next.
